Everthing you wanted to know about PanDA but were truly truly afraid to ask

### 2017-01-10 bckground.tex
Questions about PANDA and Monte Carlo workflow

>>>>

\begin{itemize}
    \item Does each job of a PANDA Server (and therefore all the tasks of that specific job) belong to the same `user'/VO?
    \item Does a PANDA Pilot pull jobs/tasks from a PANDA Server or does a PANDA server push jobs/tasks to a PANDA Pilot?
    \item Does a PANDA Pilot pull jobs or tasks from a PANDA Server? Are the jobs within a PANDA Pilot the same jobs (i.e., the same container of the same tasks) in the PANDA Server?
    \item Do we have 16 PANDA Pilots on a Titan DSL (is this the right acronym?) node? How many DSL nodes?
    \item Can the events packaged into a PBS job belong to different submissions, i.e., different jobs, i.e., different users?
    \item Do we have the distribution of the time taken on titan to process 1 event of the Monte Carlo workflow?
\end{itemize}
